Toggle Smell Detection in Google Chrome

### 2015-12-08 paper/paper.tex

@@

\subsection{Verification of results}
\label{Result Varification}
Except for the module “chrome”, we manually verified and confirmed that smells reported by algorithm are indeed presence in the code and not a false positive. Also for the modules of lesser size like ppapi, where no smells were found by the detector, we manually checked the source code for potential code smells by using the eclipse search by file and search by references feature. We invoked a search by references for the API invoking the toggle method name. Though there were instances of method invocations, there were not any potential code smells observed through manual inspection.

>>>>

\begin{table*}[ht]
\caption{Number of Smells}
\centering
\begin{tabular}{|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|p{2.1cm}|}
 \hline\hline
Module Name & Num Files & Nested Toggle \#Smells & Spread Toggle \#Smells & Combinatorial Toggle \#Smells &  Dead Toggle \#Smells & Average time to scan/Smell \\ \hline

Base & 749 & 1 & 5 & 4  & 0 & 1556013 ms \\ \hline
UI & 1501 & 2 & 1 & 0  & 0 & 888080 ms \\ \hline
Net & 1534 & 16 & 0 & 9  & 0 & 927508 ms \\ \hline
Media & 746 & 16 & 0 & 9  & 0 & 370563 ms \\ \hline
ppapi & 563 & 0 & 0 & 0  & 0 & 944816 ms \\ \hline
ash & 502 & 1 & 1 & 0  & 0 & 390563 ms \\ \hline
chrome & 6105 & 109 & 31 & 24  & 0 & 2468547 ms \\ \hline

\end{tabular}
\label{table:chrome-result-data}
\end{table*}

@@

\subsection{Verification of Results}
\label{Result Varification}
Except for the module “chrome”, we manually verified and confirmed that smells reported by algorithm are indeed presence in the code and not a false positive. Also for the modules of lesser size like ppapi, where no smells were found by the detector, we manually checked the source code for potential code smells by using the eclipse search by file and search by references feature. We invoked a search by references for the API invoking the toggle method name. Though there were instances of method invocations, there were not any potential code smells observed through manual inspection.
